---
title             : "Correlation of Microelements and Bone Pathologies: A meta-analysis"
shorttitle        : "CMBP"

author: 
  - name          : "Luana-Stefana Opariuc-Dan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "University Street 16, Iasi 700115, Romania"
    email         : "luana-stefana_c_opariuc-dan@d.umfiasi.ro"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
      - Methodology
      - Validation
      - Investigation
  - name          : "Cornelia Geanina Mircea"
    affiliation   : "1"
    role:
      - Writing - Review & Editing
      - Project administration
      - Resources
      - Validation
      - Supervision
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "2"
    role:
      - Formal analysis
      - Data curation
      - Visualisation
      - Validation

affiliation:
  - id            : "1"
    institution   : "Grigore T. Popa University of Medicine and Pharmacy"
  - id            : "2"
    institution   : "University of Bucharest"

authornote: |
  Luana-Stefana Opariuc-Dan, PhD Student, Doctoral School, Faculty of Pharmacy, Department of Pharmaceutical Biochemistry and Clinical Laboratory, Grigore T. Popa University of Medicine and Pharmacy, Iasi, Romania.
  
  Cornelia Geanina Mircea, PhD Professor, Doctoral School, Faculty of Pharmacy, Department of Pharmaceutical Biochemistry and Clinical Laboratory, Grigore T. Popa University of Medicine and Pharmacy, Iasi, Romania.
  
  Cristian Opariuc-Dan, PhD Lecturer, Doctoral School, Faculty of Psychology and Educational Sciences, University of Bucharest, Romania.

abstract: |
 Osteoporosis is a condition caused by bone loss that affects people around the world. Studies show that the spine is most prone to fractures. The mature bone matrix is a complex mineralized tissue, with a structural framework composed mainly of collagen and containing a small number of proteins and non-collagenous glycoproteins, calcium phosphates but also microelements. The bone matrix is composed not only of calcium, phosphorus, magnesium, elements that have been studied so much, but also of a series of microelements such as manganese, strontium, chromium, copper, zinc [@Strause1994].  Studies of the white population show that over 50% of women and about 20% of men above the age of 60 will suffer a non-traumatic fracture of the hip, vertebral body, proximal humerus and distal forearm during the rest of their lives. There are 3.5 million new cases of osteoporosis each year in the European Union. It is desired to diagnose the disease early by specific tests for osteoporosis prevention [@Grigorie2013].

 Trace elements are mineral elements that are found in the body in very small quantities to achieve normal physiological processes. Copper, zinc and iron ensure the correct synthesis of macromolecules that form the bone structure [@Brancatella2020]. Without those microelements, the formation of new bone by osteoblasts and the degradation (resorption) of old bone by the osteoclasts, will be modified and the osteoporosis can appear. It has to be a balance between bone formation and bone resorption for the health of the bone. 
  
keywords          : "osteoporosis, trace elements, diagnosis, bone density, bone metabolism"
wordcount         : "63 words in text body, 49 words in reference section"

bibliography      : ["r-references.bib", "CMBP.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_pdf

header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
    
    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
  - \usepackage[document]{ragged2e}

---

```{r setup, include = FALSE}
  library(papaja)
  r_refs("r-references.bib")
```

```{r analysis-preferences}
  # Seed for random number generation
  set.seed(5447)
  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
Osteoporosis is a pathology involving a number of diseases in the field of endocrinology, but also genetic and nutritional causes. The intake of microelements is essential as they are enzymatic cofactors for the specific enzymes of bone metabolism [@Strause1993].  Zinc, copper, fluorine, manganese, magnesium, iron and boron are part of bone microarchitecture, but if they are deficient in childhood and adolescence, they will cause much more loss of bone tissue at menopause or old age fact that leads to osteoporosis [@Zofkova2013]. Although the optimal concentration of calcium and vitamin D plays an important role in the prevention of osteoporosis, it is a major public health problem, affecting millions of people because there is a large inadequate supply of important nutrients to the bone, and this increase the risk for bone loss. The process of bone anabolism requires an adequate and constant supply of: protein, magnesium, phosphorus, potassium and fluoride. Recently microelements have been found to play an important role in bone-related metabolic processes, including manganese, copper, boron, iron, zinc. [@Palacios2006].

Gabr S. et al 2016, observed that exercise and active lifestyle are essential for prevention of osteoporosis. The importance of copper in the formation of lysyloxidase and collagen-elastin bonds in the bone matrix has also been observed. Manganese is involved in the formation of chondroitin sulfate. Zinc is a microelement that is part of the structure of bone alkaline phosphatase and is a cofactor for collagenase. It converts procollagen into collagen, and the formation of hydroxyapatite is achieved by releasing phosphorus from the structure of bone alkaline phosphatase. [@Alghadir2016].

Zinc is an essential microelement in bone metabolism that prevents bone resorption and promotes bone reformation, through various mechanisms such as regulating the secretion of calcitonin from the thyroid gland, promoting osteoblastic activity and alkaline phosphatase, having an anabolic role in bone tissue. The data showed that zinc is deficient in the elderly population, thus preventing bone mineralization and the formation of hydroxyapatite and collagen. This leads to osteoporosis with loss of bone structure integrity and increasing the risk of non-traumatic fracture. In osteoporosis, significant concentrations of zinc in the urine are observed, especially in menopausal women [@Colpan2005]. It has been found that zinc is an essential microelement in the development of the skeletal bone since intrauterine life, its deficiency leading to abnormal changes in the fetus and postpartum. Zinc is part of the structure of over 200 enzymes, being an enzymatic cofactor for alkaline phosphatase, involved in the synthesis of some components of the bone matrix, ensures the normal synthesis of collagen playing an important role in bone mineralization. Studies have shown that zinc in optimal concentrations improves osteoblastic function, ensures the normal synthesis of collagen and proteoglycan, and increases bone deposits of calcium and magnesium. Positive correlations were found between zinc and copper deficiency and osteoporosis. Low serum copper concentrations have been identified in femoral head fractures [@Arikan2011].

Yamaguchi states the importance of zinc in the normal development of the skeleton, especially after menopause. Zinc intervenes in the cellular apoptosis of mature osteoclasts and inhibits the synthesis of osteoclast-like cells in the bone marrow. It has an inhibitory effect on the activating receptor of nuclear factor (NF) -kB ligand (RANKL) which induces osteoclastogenesis [@Yamaguchi2009]. Studies have shown that strontium can replace calcium, which is chemically very similar to calcium (@Delmas1993, @Pemmer2013). 



# Methods
A systematic literature search will be conducted in English, using the PRISMA workflow [@page_etal21], via the following databases: *PubMed, Embase, Elsevier Science Direct, MedLine, Elsevier Scopus*, and *SpringerLink*, without imposing any limitations on publication years, and the following search phrase: *"trace elements" AND osteoporosis AND (osteoclast OR osteoblast) AND (zinc OR mineralization)*.

The resulting studies will then be selected based on the following **inclusion criteria**:  The following works will be **explicitly excluded**: (1) chapters in books or encyclopedias, (2) editorials, (3) reviews and meta-analysis, (4) case studies, (5) studies conducted on animals. Duplicates will be also removed, keeping a single study.

## Quality assessment and coding
Two authors (LSOD and COD) will independently code the retained studies based on coding manual, and disagreements will be arbitrated by the third author (CGM). The same procedure will be used to evaluate the quality of the studies, using QUADAS-2 standards [@QUADAS2]. 

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

## Literature search results

## Quality assessments results

## Data analysis


# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
